---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{r}
unzip(zipfile = "activity.zip")
Data <- read.csv("activity.csv", header = T, )
library(lubridate)
Data$date1 <- ymd(Data$date)
Data$date2 <- wday(Data$date1, label = TRUE)

```


## What is mean total number of steps taken per day?

For this part of the assignment, you can ignore the missing values in the dataset.

1. Calculate the total number of steps taken per day

```{r}
library(dplyr)
Data1 <- Data %>% 
         group_by(date) %>% 
         summarise(Sum_Steps = sum(steps, na.rm = T))
Data1
```

2. If you do not understand the difference between a histogram and a barplot, research the difference between them. Make a histogram of the total number of steps taken each day

```{r}
hist(Data1$Sum_Steps, col = "red", xlab = "Sum_Steps", main = "Histogram of the total number of steps taken each day")
library(ggplot2)
ggplot(data = Data1, aes(x= Sum_Steps)) +
  geom_histogram(breaks=seq(0,max(Data1$Sum_Steps)+5000,5000),
                 fill="lightblue", colour="black")
```

3. Calculate and report the mean and median of the total number of steps taken per day

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
